Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-04-02 docs/ms.tex
Update ms.tex

\section{Introduction}
\label{sec:intro}

@@

Weak gravitational lensing has become the most potential tool to explore the dark universe. 
One application of Weak gravitational lensing is that it can be used to measure the mass profile of single galaxy,galaxy groups and clusters or large scales.
Cosmic shear is the mild distortion of distant galaxy images due to the bending of light by intervening matter.It provides one of the most promising methods for constraining the nature of dark energy (Albrecht et al. 2006; Peacock&Schneider 2006). 
While in galaxy--galaxy weaklensing ,tangential shear distortions of background galaxies around foreground galaxies, allows direct measurement of the galaxy–DM correlation

The distortion in Weak lensing is typically ~ 0.01,or ~0.001 for galaxy-galaxy lensing  it's usually more than 10 times smaller than the intrinsic shape 
noise,it's also smaller than the distortion caused be PSF effect which usually has ~0.05 level.
The main source of uncertainty of tangential shear comes from the intrinsic shape "noise" . We know little knowledge about 
the distribution of intrinsic ellipticity,exception the assumption that the orientational angle should be isotropic.
With this assumption,we can use the average of galaxies' ellipticity as an estimator of tangential shear.--However by 
doing this we lose some information about how the ellipticity are distributed. Simple average point estimator can't 
use the other reasonable assumption about intrinsic shape distribution --galaxies in different sky patches should have 
the same shape distibution--which is the result of homogeneous Universe.

@@

In galaxy--galaxy lensing ,since the distortion is so weak,what people usually do is stack many lensing signals together and get the "average"
shear map,and then infers the mean mass profile of galaxy or galaxy cluster.
However with HB method we can avoid this brute averaging ,instead we can get the posterior distribution of mass profile for 
each lensing system - even though it has very large uncertainty- we can calculate the statistical property like galaxy-mass
correlation function via this posterior distribution.

@@

\section{method}
\label{sec:XXX}

@@

and it's inverse formula 
\begin{equation}
\epsilon_{0}=\frac{\epsilon_{\ell}-g}{1-g^{*}\epsilon_{\ell}}
\end{equation}
from Schramm \& Kayser (1995), Seitz \& Schneider (1997), where $\epsilon$
is represented as a complex variable and g, $g^{*}$ are the reduced
shear and its complex conjugate, respectively. $\epsilon$ is defined
in terms of the major and minor axes and orientation a, b, $\phi$,
respectively, as $\epsilon$ = (a − b)/(a + b) exp(2i$\phi$). Due to the isotropicity
of Universe ,we expect $\phi$ has a uniform distribution from 0 to
$\pi$.Then we can expect 
\begin{equation}
<\epsilon_{\ell}>=g
\end{equation}

@@

\begin{equation}
p(\epsilon_{\ell}|\vec{g},\alpha)=p(\epsilon_{0}(\vec{g})|\alpha)*|\frac{\partial\epsilon_{0}}\,{\partial\epsilon_{\ell}}|
\end{equation}

@@

If there is measurement error on $\epsilon_{ob}$,we will have 
\begin{equation}
p(\epsilon_{ob}|\vec{g},\alpha)=\int f(\epsilon_{ob}|\epsilon_{\ell})\,p(\epsilon_{\ell}|\vec{g},\alpha)
\end{equation}
Here the prior distribtuion we use for $\vec{g}$ is a 2D flat distribution
in the region $|g|<1$.Therefore $p(\vec{g)}=\begin{cases}
1 & |\vec{g}|<1\\
0 & |\vec{g}|>1
\end{cases}$

@@

Since $p(\alpha)$ does not explicitly depends on $\vec{g}$ .$p(\alpha|\vec{g})$is
just the pror distribution $p(\vec{\alpha}|\xi)$.Therefore,we have marginalized likehood
\begin{equation}
p(\epsilon_{\ell}|\vec{g})=\int p(\epsilon_{\ell}|\vec{g},\alpha)\,p(\vec{\alpha}|\xi)d\alpha
\end{equation}
Given that marginalized likelihood function ,in principle we could optimize it  and gives out a max-likelihood estimator 
for \vec{g} in different patches simultaneously.

@@

While making the posterior samples $p(\g,\alpha|Data)$ we choose to use the classical
Gibbs sampler.

@@

\section{Result}
\label{sec:XXX}

\subsection{Posterior samples}
We show the posterior samples of both g and $\alpha$ ,for both beta function and step function model.
\subsection{Bias Test}
We test the systematical bias of our estimator.(Here the estimator is the max-marginalized likelihood estimator?)
We plot $g_{1}-g_{1}^{true}$ VS $g_{1}^{true}$ ,and put on an error bar which equals standard deviation of 
marginalized likehood functon $p(Data|g_{1})$ ,and use a linear fit to determin the m,c value and their standard 
deviations.

\subsection{Accuracy Test}
We compare the mean square error of our estimator with average and the estimator that could be constructed if the true unlensed
ellipticity distribution were known.
We show how the mean square error varies with number of galaxies ,number of patches and so on.

\subsection{Measurement Error}
We show some example how our method works when there is an Gaussian noise added on the observed $\epsilon$

\subsection{prefactor $\xi$}
Discuss about how $\xi$ is tuned ,the danger if $\xi$ is set to be too large or too small.

@@

\section{Discussion}
\label{sec:XXX}
In weak lensing survey,one way to obtain high S/N ratio is to stack large number of lensing signal together,and 
calculate the mean shear map of all these lensing systems.However simply to stack all the lensing signals would not be the
optimal way because of the amount of information we can obtain from each lensing system can be very different.
The Bayesian inference approach we proposed allows a natural way to optimally include all the data.In stead of stacking what we need to do
is to propogate the likelihood of the shear map of each lensing system. The statistical property of all the lensing systems
like the galaxy-mass ,shear-shar correlation function ,in principle can be calculated from these likelihood functions.

@@

\section{Discussion}
\label{sec:discuss}

@@

\section{Conclusions}
\label{sec:conclusions}

In summary,We have presented a conceptually simple method for estimating tangential shear ,
with carefully calculated uncertainty estimates. This method is intrinsically cope with high noise levels on the input data and naturally
allows bad fit to be identified from the residuals map.
We have proposed an exceeding flexible model for intrinsic shape distribution allows us to obtain the correct posterior distributions,
while avoiding making unsupported assumptions.The Gibbs sampler allows us to sample the posterior distribution of shear in 
large number of sky patches simultaneously and efficiently.

\begin{itemize}

\item We ...

\item The ...

\item The ...

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  ACKNOWLEDGMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\section{Introduction}

\label{sec:intro}

@@

Weak gravitational lensing has become the most potential tool to explore
the dark universe. One application of Weak gravitational lensing is
that it can be used to measure the mass profile of single galaxy,galaxy
groups and clusters or large scales. Cosmic shear is the mild distortion
of distant galaxy images due to the bending of light by intervening
matter.It provides one of the most promising methods for constraining
the nature of dark energy (Albrecht et al. 2006; Peacock\&Schneider
2006). While in galaxy--galaxy weaklensing ,tangential shear distortions
of background galaxies around foreground galaxies, allows direct measurement
of the galaxy-DM correlation

The distortion in Weak lensing is typically ~ 0.01,or ~0.001 for
galaxy-galaxy lensing it's usually more than 10 times smaller than
the intrinsic shape noise,it's also smaller than the distortion caused
be PSF effect which usually has ~0.05 level. For shear measurement
the main source of uncertainty comes from the intrinsic shape noise
. We know little knowledge about the distribution of intrinsic ellipticity,exception
the assumption that the orientational angle should be isotropic. With
this assumption,we can use the average of galaxies' ellipticity as
an estimator of tangential shear.--However by doing this we lose some
information about how the ellipticity are distributed. Simple average
point estimator can't use the other reasonable assumption about intrinsic
shape distribution --galaxies in different sky patches should have
the same shape distibution--which is the result of homogeneous Universe.

@@

In galaxy--galaxy lensing ,since the distortion is so weak,what people
usually do is stack many lensing signals together and get the mean
shear map,and then infers the mean mass profile of galaxy or galaxy
cluster. However with HB method we can avoid this brute averaging
,instead we can get the posterior distribution of mass profile for
each lensing system - even though it has very large uncertainty- we
can calculate the statistical property like galaxy-mass correlation
function via this posterior distribution.

@@

\section{method}

\label{sec:XXX}

@@

and it's inverse formula 
\begin{equation}
\epsilon_{0}=\frac{\epsilon_{\ell}-g}{1-g^{*}\epsilon_{\ell}}
\end{equation}
from Schramm \& Kayser (1995), Seitz \& Schneider (1997), where $\epsilon$
is represented as a complex variable and g, $g^{*}$ are the reduced
shear and its complex conjugate, respectively. $\epsilon$ is defined
in terms of the major and minor axes and orientation a, b, $\phi$,
respectively, as $\epsilon$ = (a - b)/(a + b) exp(2i$\phi$). Due
to the isotropicity of Universe ,we expect $\phi$ has a uniform distribution
from 0 to $\pi$.Then we can expect 
\begin{equation}
<\epsilon_{\ell}>=g
\end{equation}

@@

\begin{equation}
p(\epsilon_{\ell}|\vec{g},\alpha)=p(\epsilon_{0}(\vec{g})|\alpha)*|\frac{\partial\epsilon_{0}}{\,}{\partial\epsilon_{\ell}}|
\end{equation}

@@

If there is measurement error on $\epsilon_{ob}$,we will have 
\begin{equation}
p(\epsilon_{ob}|\vec{g},\alpha)=\int f(\epsilon_{ob}|\epsilon_{\ell})\, p(\epsilon_{\ell}|\vec{g},\alpha)
\end{equation}
Here the prior distribtuion we use for $\vec{g}$ is a 2D flat distribution
in the region $|g|<1$.Therefore $p(\vec{g)}=\begin{cases}
1 & |\vec{g}|<1\\
0 & |\vec{g}|>1
\end{cases}$

@@

Since $p(\alpha)$ does not explicitly depends on $\vec{g}$ .$p(\alpha|\vec{g})$is
just the pror distribution $p(\vec{\alpha}|\xi)$.Therefore,we have
marginalized likehood 
\begin{equation}
p(\epsilon_{\ell}|\vec{g})=\int p(\epsilon_{\ell}|\vec{g},\alpha)\, p(\vec{\alpha}|\xi)d\alpha
\end{equation}
Given that marginalized likelihood function ,in principle we could
optimize it and gives out a max-likelihood estimator for $\vec{g}$
in different patches simultaneously.

@@

While making the posterior samples $p(g,\alpha|Data)$ we choose to
use the classical Gibbs sampler.

@@

\section{Result}

\label{sec:XXX}

\subsection{Posterior samples}

We show the posterior samples of both g and $\alpha$ ,for both beta
function and step function model.

\subsection{Bias Test}

We test the systematical bias of our estimator.(Here the estimator
is the max-marginalized likelihood estimator?) We plot $g_{1}-g_{1}^{true}$
VS $g_{1}^{true}$ ,and put on an error bar which equals standard
deviation of marginalized likehood functon $p(Data|g_{1})$ ,and use
a linear fit to determin the m,c value and their standard deviations.

\subsection{Accuracy Test}

We compare the mean square error of our estimator with average and
the estimator that could be constructed if the true unlensed ellipticity
distribution were known. We show how the mean square error varies
with number of galaxies ,number of patches and so on.

\subsection{Measurement Error}

We show some example how our method works when there is an Gaussian
noise added on the observed $\epsilon$

\subsection{prefactor $\xi$}

Discuss about how $\xi$ is tuned ,the danger if $\xi$ is set to
be too large or too small.

@@

\section{Discussion}

\label{sec:XXX} In weak lensing survey,one way to obtain high S/N
ratio is to stack large number of lensing signal together,and calculate
the mean shear map of all these lensing systems.However simply to
stack all the lensing signals would not be the optimal way because
of the amount of information we can obtain from each lensing system
can be very different. The Bayesian inference approach we proposed
allows a natural way to optimally include all the data.In stead of
stacking what we need to do is to propogate the likelihood of the
shear map of each lensing system. The statistical property of all
the lensing systems like the galaxy-mass ,shear-shar correlation function
,in principle can be calculated from these likelihood functions.

@@

\section{Discussion}

\label{sec:discuss}

@@

\section{Conclusions}

\label{sec:conclusions}

In summary,We have presented a conceptually simple method for estimating
tangential shear , with carefully calculated uncertainty estimates.
This method is intrinsically cope with high noise levels on the input
data and naturally allows bad fit to be identified from the residuals
map. We have proposed an exceeding flexible model for intrinsic shape
distribution allows us to obtain the correct posterior distributions,
while avoiding making unsupported assumptions.The Gibbs sampler allows
us to sample the posterior distribution of shear in large number of
sky patches simultaneously and efficiently.
\begin{itemize}
\item We ...
\item The ...
\item The ...
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  ACKNOWLEDGMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
